Adaptive evolution with aneuploidy and mutation

### 2022-05-06 ms/ms.tex
small TODO was added

%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Evolutionary Model.}
We model the evolution of a population of cells using a Wright-Fisher model~\citep{Otto2007}, assuming a constant effective population size $N$, non-overlapping generations, and including the effects of natural selection, genetic drift, aneuploidy, and mutation. 
We focus on beneficial genetic modifications, neglecting the effects of deleterious and neutral mutations or karyotypic changes.
The model allows for a single aneuploid karyotype (e.g., chromosome III duplication) and a single mutation to accumulate in the genotype.
Thus, the model follows four genotypes~(\Cref{fig:models}): euploid wild-type, \euwt, the initial genotype; 
euploid mutant, \eumt, with the standard karyotype and a single beneficial mutation; 
aneuploid wild-type, \anwt, with an extra chromosome, i.e., following chromosome duplication; and
aneuploid mutant, \anmt, with and extra chromosome and a beneficial mutation.

@@

\begin{figure}[p]
  \centering
\includegraphics[width=0.8\textwidth]{../figures/dynamics.pdf}
  \caption{
  \textbf{Posterior genotype frequency dynamics for the model.} 
  The posterior prediction for the frequencies of the four genotypes over time. Each of the 20 curves is the average of 10,000 simulations of the model using parameters drawn from the posterior distribution.
  }
  \label{fig:ppc-plot}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Evolutionary Model.}
We model the evolution of a population of cells using a Wright-Fisher model~\citep{Otto2007}, assuming a constant effective population size $N$, %TODO we need to write in some place that it is 6.425*10**6 in our simulations: 1.6M to 2004.8M in Yona experiment
 non-overlapping generations, and including the effects of natural selection, genetic drift, aneuploidy, and mutation. 
We focus on beneficial genetic modifications, neglecting the effects of deleterious and neutral mutations or karyotypic changes.
The model allows for a single aneuploid karyotype (e.g., chromosome III duplication) and a single mutation to accumulate in the genotype.
Thus, the model follows four genotypes~(\Cref{fig:models}): euploid wild-type, \euwt, the initial genotype; 
euploid mutant, \eumt, with the standard karyotype and a single beneficial mutation; 
aneuploid wild-type, \anwt, with an extra chromosome, i.e., following chromosome duplication; and
aneuploid mutant, \anmt, with and extra chromosome and a beneficial mutation.

@@

% Fig dynamics
%% generated with dynamics-plot.ipynb
\begin{figure}[p]
  \centering
\includegraphics[width=0.8\textwidth]{../figures/dynamics.pdf}
  \caption{
  \textbf{Posterior genotype frequency dynamics for the model.} 
  The posterior prediction for the frequencies of the four genotypes over time. Each of the 20 curves is the average of 10,000 simulations of the model using parameters drawn from the posterior distribution.
  }
  \label{fig:ppc-plot}
\end{figure}
